---
title: "weighted-frequencies"
format: html
editor: visual
---

# Load packages
```{r}
library(tidyverse)
```

# Functions needed for the merging

```{r}
text_matrix <- function(dat, table_title) {
  rbind(rep('', ncol(dat)),
        c(table_title, rep('', ncol(dat)-1)), # title
        rep('', ncol(dat)), # blank spacer row
        names(dat), # column names
        unname(sapply(dat, as.character))) # data

}
```

# prepare the data
## Drop Transgender 
```{r}
df_ana <- df_incu_india_raw %>% 
  filter(A2 != "Transgender")
```

## Subset data
```{r}
df_bihar <- df_ana %>% filter(State == "Bihar")
df_up <- df_ana %>% filter(State == "Uttar Pradesh")
df_maha <- df_ana %>% filter(State == "Maharashtra")
df_list <- list(df_bihar, df_up, df_maha, df_ana)
```

# Create Lists for the loop
## List of survey objects
```{r}
library(survey)
## Define Survey Object for each state
svy.obj_bihar <- survey::svydesign(ids = ~1, data = df_bihar, weights = df_bihar$w_overall)
svy.obj_up <- survey::svydesign(ids = ~1, data = df_up, weights = df_up$w_overall)
svy.obj_maha <- survey::svydesign(ids = ~1, data = df_maha, weights = df_maha$w_overall)
svy.obj_full <- survey::svydesign(ids = ~1, data = df_ana, weights = df_ana$w_overall)
## List of survey objects
svy_obj_list <- list(svy.obj_bihar, svy.obj_up, svy.obj_maha, svy.obj_full)
```

## List of variables in each section
```{r}
sec_a <- c("A5", "A6", "A7", "A9", "A14", "A16", "A17")
sec_b <- c("B1", "B3", "B4", "B4X", "B5", "B6", "B7", "B8", "B9", "B10", "B11", 
           "B12", "B12X", "B12M", "B12XM", "B14a", "B14b", "B14c", "B14d")
sec_c <- c("C1", "C2", "C3", "C4", "C5", "C7", "C8", "C9", "C10", 
            "C11", "C12", "C13", "C13X", "C14", "C15", "C16_1", "C16_2", 
            "C17", "C18", "C19", "C20", "C21", "C22", "C23a", "C23b", 
            "C23c", "C23d", "C23e", "C23f", "C23g", "C23h", "C23i", "C23j", 
             "C23l", "C24", "C25", "C26", "C27", "C28", "C29", "C30a", "C30b",
              "C30c", "C30d", "C31", "C32", "C33a", "C33b", "C33c", "C33d", 
               "C33e", "C33f", "C33g", "C33h", "C33i", "C33j", "C33k", "C33l")
sec_d <- c("D1", "D4", "D6", "D7", "D6X", "D7X", "D8", "D9a", "D9b", 
            "D9c", "D9d", "D9e", "D10", "D10a", "D10b", "D10c", 
                        "D10d", "D10e", "D10Xa", "D10Xb", "D10Xc", "D10Xd", "D10Xe", 
                        "D11a", "D11b", "D11c", "D11d", "D11e", "D12", "D13")
sec_e <- c("E1", "E3", "E4", "E5a", "E5b", "E5c", "E5d", "E6", "E7", "E8", 
            "E10", "E11", "E12", "E13", "E14")
sec_f <- c("F1a", "F1b", "F1c", "F1d", "F1e", "F1f", "F1g", "F1h", "F1i", 
          "F1j", "F2", "F3", "F4", "F5", "F6", "F7", "F8", "F9", "F10", "F11", 
          "F12a", "F12b", "F12c", "F12d", "F12e", "F12f", "F12g", "F12h", 
          "F12i", "F12j", "F12k", "F12l", "F12m", "F12n", "F13")
sec_g <- c("G1" , "G2" , "G3" , "G4" , "G5a" , "G5b" , "G5c" , "G5d" , "G5e" , "G5f" , 
                "G5g" , "G5h" , "G5i" , "G5j" , "G5k" , "G5l" , "G6a" , "G6b" , "G6c" ,
                 "G6d" , "G6e" , "G6f" , "G6g" , "G6h" , "G6i" , "G6j" , "G6k" , "G6l" , "G7a_1" ,
                  "G7a_2" , "G7a_3" , "G7a_4" , "G7a_5" , "G7b_1" , "G7b_2" , "G7b_3" ,
                   "G7b_4" , "G7b_5" , "G7c_1" , "G7c_2" , "G7c_3" , "G7c_4" , "G7c_5" ,
                    "G7d_1" , "G7d_2" , "G7d_3" , "G7d_4" , "G7d_5" , "G7e_1" , "G7e_2" ,
                     "G7e_3" , "G7e_4" , "G7e_5" , "G7f_1" , "G7f_2" , "G7f_3" , "G7f_4" ,
                    "G7f_5" , "G7g_1" , "G7g_2" , "G7g_3" , "G7g_4" , "G7g_5" , "G7h_1" ,
                     "G7h_2" , "G7h_3" , "G7h_4" , "G7h_5" , "G7i_1" , "G7i_2" , "G7i_3" ,
                      "G7i_4" , "G7i_5" , "G7j_1" , "G7j_2" , "G7j_3" , "G7j_4" , "G7j_5" ,
                "G7k_1" , "G7k_2" , "G7k_3" , "G7k_4" , "G7k_5" , "G7l_1" , "G7l_2" ,
                "G7l_3" , "G7l_4" , "G7l_5" , "G7Xa_1" , "G7Xa_2" , "G7Xa_3" ,
                "G7Xa_4" , "G7Xa_5" , "G7Xa_6" , "G7Xb_1" , "G7Xb_2" , "G7Xb_3" ,
                "G7Xb_4" , "G7Xb_5" , "G7Xb_6" , "G7Xc_1" , "G7Xc_2" , "G7Xc_3" ,
                  "G7Xc_4" , "G7Xc_5" , "G7Xc_6" , "G7Xd_1" , "G7Xd_2" , "G7Xd_3" , 
                   "G7Xd_4" , "G7Xd_5" , "G7Xd_6" , "G7Xe_1" , "G7Xe_2" , "G7Xe_3" ,
                    "G7Xe_4" , "G7Xe_5" , "G7Xe_6" , "G7Xf_1" , "G7Xf_2" , "G7Xf_3" ,
                     "G7Xf_4" , "G7Xf_5" , "G7Xf_6" , "G7Xg_1" , "G7Xg_2" , "G7Xg_3" , 
                        "G7Xg_4" , "G7Xg_5" , "G7Xg_6" , "G7Xh_1" , "G7Xh_2" , "G7Xh_3" , 
                        "G7Xh_4" , "G7Xh_5" , "G7Xh_6" , "G7Xi_1" , "G7Xi_2" , "G7Xi_3" , 
                        "G7Xi_4" , "G7Xi_5" , "G7Xi_6" , "G7Xj_1" , "G7Xj_2" , "G7Xj_3" , 
                        "G7Xj_4" , "G7Xj_5" , "G7Xj_6" , "G7Xk_1" , "G7Xk_2" , "G7Xk_3" , 
                        "G7Xk_4" , "G7Xk_5" , "G7Xk_6" , "G7Xl_1" , "G7Xl_2" , "G7Xl_3" , 
                        "G7Xl_4" , "G7Xl_5" , "G7Xl_6" , "G8a" , "G8b" , "G8c" , "G8d" , 
                  "G8e" , "G8f" , "G8g" , "G8h" , "G8i" , 
                        "G8j" , "G8k" , "G8l" , "G9a" , "G9b" , "G9c" , "G9d" , "G9e" , "G9f" , 
                        "G9g" , "G9h" , "G9i" , "G9j" , "G9k" , "G9l" , "G10a_1" , "G10a_2" , 
                        "G10a_3" , "G10a_4" , "G10b_1" , "G10b_2" , "G10b_3" , "G10b_4" , 
                        "G10c_1" , "G10c_2" , "G10c_3" , "G10c_4" , "G10d_1" , "G10d_2" , 
                        "G10d_3" , "G10d_4" , "G10e_1" , "G10e_2" , "G10e_3" , "G10e_4" , 
                        "G10f_1" , "G10f_2" , "G10f_3" , "G10f_4" , "G10g_1" , "G10g_2" , 
                        "G10g_3" , "G10g_4" , "G10h_1" , "G10h_2" , "G10h_3" , "G10h_4" , 
                        "G10i_1" , "G10i_2" , "G10i_3" , "G10i_4" , "G10j_1" , "G10j_2" , 
                        "G10j_3" , "G10j_4" , "G10k_1" , "G10k_2" , "G10k_3" , "G10k_4" , 
                        "G10l_1" , "G10l_2" , "G10l_3" , "G10l_4" , "G10Xa_1" , "G10Xa_2" , 
           "G10Xa_3" , "G10Xa_4" , "G10Xa_5" , 
                        "G10Xb_1" , "G10Xb_2" , "G10Xb_3" , "G10Xb_4" , "G10Xb_5" , 
                        "G10Xb_6" , "G10Xc_1" , "G10Xc_2" , "G10Xc_3" , "G10Xc_4" , 
                        "G10Xc_5" , "G10Xd_1" , "G10Xd_2" , "G10Xd_3" , "G10Xd_4" , 
                        "G10Xd_5" , "G10Xe_1" , "G10Xe_2" , "G10Xe_3" , "G10Xe_4" , 
                        "G10Xe_5" , "G10Xf_1" , "G10Xf_2" , "G10Xf_3" , "G10Xf_4" , 
                        "G10Xf_5" , "G10Xg_1" , "G10Xg_2" , "G10Xg_3" , "G10Xg_4" , 
                        "G10Xg_5" , "G10Xh_1" , "G10Xh_2" , "G10Xh_3" , "G10Xh_4" , 
                        "G10Xh_5" , "G10Xi_1" , "G10Xi_2" , "G10Xi_3" , "G10Xi_4" , 
                        "G10Xi_5" , "G10Xj_1" , "G10Xj_2" , "G10Xj_3" , "G10Xj_4" , 
                        "G10Xj_5" , "G10Xk_1" , "G10Xk_2" , "G10Xk_3" , "G10Xk_4" , 
                        "G10Xk_5" , "G10Xl_1" , "G10Xl_2" , "G10Xl_3" , "G10Xl_4" , 
                        "G10Xl_5" , "G11" , "G12")
sec_h_i <- c("H1" , "H2_1" , "H2_2" , "H2_3" , "H2_4" , "H2_5" , "H2_6" , "H3_1" , 
              "H3_2" , "H3_3" , "H3_4" , "H3_5" , "H4a" , "H4b" , "H4c" , "H4d" , "H4e" , 
              "H4f" , "I1")

```





# Write a function to generate state and sex disaggregated weighted frequencies by Section
## Note to self: run the code chunk below for different sections by changing the section names in the for loop for i and change the name of the file in the write.csv command at the end
```{r}
######## This works for the core function
df_col <- NULL
  # Start a loop for all survey objects by State
  for (svy in svy_obj_list) { 
  # Counter to reset the dataset for individual states
  df_rows <- NULL
    for (i in sec_d) {
  # Create a single crosstab for  one variable by Sex
    a1 <- svytable(~get(i) + A2, design = svy) %>% 
    prop.table(2) %>% 
    magrittr::multiply_by(100) %>% 
    round(digits = 2) %>% 
    as.data.frame.array() %>% 
    mutate(Categories = rownames(.)) %>% 
    mutate("Female (N)" = with(svy$variables, table(get(i), A2))[,1]) %>% 
    mutate("Male (N)" = with(svy$variables, table(get(i), A2))[,2]) %>% 
    select(Categories, "Female (N)", "Female (%)" = Female, "Male (N)", "Male (%)" = Male) 
  
  # call the text matrix function to add a label for each variable  
  temp <- text_matrix(a1, label(df_ana[[i]]))
  # Bind all variables within a section 
  df_rows <- rbind(df_rows, temp)
    }
  df_col <- cbind(df_col, df_rows)
  }
write.csv(df_col, file = "./outputs/weighted-freq/sec-d_new.csv", row.names = F, col.names = F)
```
